opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-26 chapters/02_existing_datasets.tex
Added links to other crystal structure resources.

There is also much publicly available powder diffraction data uploaded to datasets on Zenodo. However, this data is split into disparate entries that typically only contain the work of a single research project. Additionally, extracting powder diffraction data at scale is hindered by the fact that the data is often given in plain text files in non-standardized formats, which are difficult to parse programmatically. Some major crystal structure databases, such as the ICSD, do not appear in the above list, as they do not include powder diffraction data. This is because most structure solutions are achieved through single-crystal diffraction rather than powder diffraction.

>>>>

There is also much publicly available powder diffraction data uploaded to datasets on Zenodo. However, this data is split into disparate entries that typically only contain the work of a single research project. Additionally, extracting powder diffraction data at scale is hindered by the fact that the data is often given in plain text files in non-standardized formats, which are difficult to parse programmatically. \\

Aside from the databases mentioned above, we have also investigated several other crystal structure resources in search of experimental powder diffraction data. Crystal structure resources that were investigated but not found to contain any appreciable amount of publicly available experimental powder diffraction data include the Inorganic Crystal Structure Database,\footnote{\url{https://icsd.products.fiz-karlsruhe.de/}}   Cambridge Structural Database,\footnote{\url{https://www.ccdc.cam.ac.uk/structures/}}  the Materials Project database,\footnote{\url{https://next-gen.materialsproject.org/}}  the Crystallographic and Crystallochemical Database\footnote{\url{https://database.iem.ac.ru/mincryst/index.php}},  the Bilbao Incommensurate Crystal Structure Database,\footnote{\url{https://www.cryst.ehu.eus/bincstrdb/search/}}  the Mineralogy Database,\footnote{\url{https://webmineral.com/}} IUCr Raw data letters,\footnote{\url{https://iucrdata.iucr.org/x/index.html}} and U.S. Naval Research Laboratory Crystal Lattice-Structures,\footnote{\url{https://www.atomic-scale-physics.de/lattice/}} the Athena Mineral database \footnote{\url{https://athena.unige.ch/athena/mineral/mineral.html}} and the Protein data bank \footnote{\url{https://www.rcsb.org/}}. This is to be expected as most structure solutions are achieved through single-crystal diffraction rather than powder diffraction.\\
